### 2023-02-02 manuscript.tex
more FDO framework [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/0bcef85d5aab4a6e854dce169024b4d2b2f36598.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/0bcef85d5aab4a6e854dce169024b4d2b2f36598/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4076361303

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/752f19bbb05f04e1d3a3cb2f18122c2e8ba953c7/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/752f19bbb05f04e1d3a3cb2f18122c2e8ba953c7}{stain/2022-fdo-paper@752f19b}
on February 2, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/0bcef85d5aab4a6e854dce169024b4d2b2f36598/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/0bcef85d5aab4a6e854dce169024b4d2b2f36598}{stain/2022-fdo-paper@0bcef85}
on February 2, 2023.
